### 2022-07-09 README.Rmd
adding vignette
README updated

## Overview
The R package **melt** provides a unified framework for data analysis with empirical likelihood methods. A collection of functions are available for regression analysis and hypothesis testing. Much of its functionality and syntax mimics the corresponding base R functions. The core computational routines are implemented with the 'Eigen' C++ library and 'RcppEigen' interface, with OpenMP for parallel computation. Additional functions are available for multiple testing for the analysis of experimental designs. Details of the testing procedures are given in [Kim, MacEachern, and Peruggia (2021)](https://arxiv.org/abs/2112.09206).

@@

## Usage
```{r eval = TRUE}
library(melt)
# one sample test for mean
fit1 <- el_mean(rnorm(n = 100), par = 0)
confint(fit1)

# linear regression
fit2 <- el_lm(mpg ~ wt, data = mtcars)
summary(fit2)
confint(fit2)

# analysis of variance 
data("clothianidin")
fit3 <- el_lm(clo ~ -1 + trt, data = clothianidin)
summary(fit3)
confint(fit3)

# test of no treatment effect
lhs <- matrix(c(1, -1, 0, 0,
                0, 1, -1, 0,
                0, 0, 1, -1), byrow = TRUE, nrow = 3)
elt(fit3, lhs = lhs)

# logistic regression
fit4 <- el_glm(vs ~ mpg, data = mtcars, family = binomial)
summary(fit4)
```

>>>>

## Overview
The R package **melt** provides a unified framework for data analysis with empirical likelihood methods. A collection of functions are available for regression analysis and hypothesis testing. The core computational routines are implemented with the 'Eigen' C++ library and 'RcppEigen' interface, with OpenMP for parallel computation. Details of the testing procedures are given in [Kim, MacEachern, and Peruggia (2021)](https://arxiv.org/abs/2112.09206).

@@

## Usage
```{r usage, eval = TRUE}
library(melt)

# Test for the mean
data("precip")
fit <- el_mean(precip, par = 30)
fit

# Linear regression
data("mtcars")
fit2 <- el_lm(mpg ~ disp + hp + wt + qsec, data = mtcars)
summary(fit2)
cr <- confreg(fit2, parm = c("disp", "hp"), npoints = 200)
plot(cr)

# Analysis of variance 
data("clothianidin") 
fit3 <- el_lm(clo ~ -1 + trt, data = clothianidin)
summary(fit3)
confint(fit3)

# Test of no treatment effect
lhs <- matrix(c(1, -1, 0, 0,
                0, 1, -1, 0,
                0, 0, 1, -1), byrow = TRUE, nrow = 3)
elt(fit3, lhs = lhs)
```
